Should geophysicists use gravity anomaly or gravity disturbance?

### 2018-05-11 manuscript/letter.tex
Revised Normal Earth section
I reordered some of the phrases to have the fact that the internal
density is not specified setup the section about geodesy not caring
about that.

Removed the part about "normal density" because it's never mentioned
again in the text.

Traditionally, the Earth's gravity field is approximated
by the gravity field produced by a reference ellipsoid
(or level ellipsoid), which is a rigid and geocentric model.
This reference ellipsoid has the minor axis $b$
coincident with the mean rotating axis of the Earth $Z$, the
same total mass (including the atmosphere) and also the
same angular velocity of the Earth \citep{heiskanen-moritz1967,
vanicek1987,hofmann-wellenhof-moritz2005,torge2012}.
Another characteristic of this model is that its
limiting surface coincides with a particular equipotential
of its own gravity field.
Here, we follow \citep{torge2012} and call this model as
\textit{normal Earth}.

The resultant of the virtual
gravitational and centrifugal forces exerted by the normal
Earth on a body at rest at a point $P$ is called
\textit{normal gravity vector} and its intensity is called
\textit{normal gravity}.
In geodesy, any model used to represent the normal gravity field
can be arbitrarily defined for the only purpose
of keeping the difference from the actual gravity field as small
as possible \citep{vanicek1987}.
It is worth noting that, although the normal Earth has the
same total mass (including the atmosphere) of the Earth,
its internal density distribution is unknown.
The search for physically meaningful mass distributions
that generate a required normal gravity field
has geophysical rather than geodetic motives \citep{marussi1974}.
The only condition imposed on its internal density
distribution is that it produces a gravity field
having a particular equipotential which coincides
with its limiting surface.
For convenience, we denote any density distribution
satisfying this condition as a \textit{normal density distribution}.

>>>>

The Earth's gravity field is traditionally approximated
by the gravity field of a reference ellipsoid (or level ellipsoid).
This model is rigid and geocentric,
with a minor axis $b$ which coincides with
the mean rotation axis of the Earth $Z$.
The ellipsoid has the same total mass as the Earth (including the atmosphere)
and also the same angular velocity \citep{heiskanen-moritz1967,
vanicek1987,hofmann-wellenhof-moritz2005,torge2012}.
Its limiting surface coincides with
a particular equipotential of its own gravity field.
Here, we follow \citep{torge2012} and call this reference ellipsoid
the \textit{normal Earth}.
Analogously to the Earth, the \textit{normal gravity vector} is
the sum of the
gravitational and centrifugal accelerations exerted by the normal
Earth on a body at rest at a point $P$.
The intensity of the normal gravity vector is called \textit{normal gravity}.

It is worth noting that, although the normal Earth has the same total mass as
the Earth, its internal density distribution is left unspecified.
The search for geologically meaningful density distributions
for the interior of the normal Earth has
geophysical rather than geodetic motives \citep{marussi1974}.
In physical geodesy, a model for the normal gravity field
can be arbitrarily defined with the sole purpose of
keeping the difference from the actual gravity field
as small as possible \citep{vanicek1987}.
The only condition imposed on its internal density
distribution is that it produces a gravity field
having a particular equipotential which coincides
with its limiting surface.
